\documentclass[aspectratio=169,colorlinks]{beamer}
\usetheme{Boadilla} % plainest one with slide number footer
% The empty linkcolor is mainly to not have a non-matching color in the presentation name in the footer
\hypersetup{colorlinks,linkcolor=,urlcolor=blue!50!black}

% generic packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{verbatim}
\usepackage{amsmath}

% about the presentation
\title{Outcome and outlook of the Friday T2TRG meeting}
\subtitle[]{
  \texttt{draft-core-transport-indication},
  \texttt{draft-amsuess-coap-over-gatt},
  \texttt{draft-core-resource-directory-extensions},
  \texttt{draft-t2trg-onion-coap}\\
  … all about Naming Things
}
\author{Christian~Amsüss}
\date{IETF118 Prague, CoRE, 2023-11-09}

% This should be my "always used in presentations" git module
\newcommand{\rfc}[1]{\href{https://datatracker.ietf.org/doc/html/rfc#1}{RFC~#1}}
\newcommand{\ietfdraft}[1]{\href{https://datatracker.ietf.org/doc/draft-#1/}{draft #1}}

% attach self

\usepackage{embedfile}
\embedfile{\jobname.tex}
\embedfile{Makefile}

\begin{document}

\frame{\titlepage}

\begin{frame}{Orientation}\large
  \begin{description}
    \item[Origin:] \rfc{8323} introducing \texttt{coap+tcp://}
    \item[led to:] \ietfdraft{silverajan-core-coap-protocol-negotiation} (stalled)
    \item[used by:] {\footnotesize \ietfdraft{bormann-t2trg-slipmux} (\texttt{coap+uart://}), \ietfdraft{amsuess-core-coap-over-gatt} (\texttt{coap+gatt://}), \ietfdraft{becker-core-coap-sms-gprs} (\texttt{coap+sms://})}
    \item[reboot:] \ietfdraft{ietf-core-transport-indication} -- \texttt{rel=has-proxy}
    \item[more users:] \ietfdraft{amsuess-t2trg-rdlink}, \ietfdraft{amsuess-t2trg-onion-coap} (both \texttt{coap://encodedpublickey.tbd.arpa})

      \bigskip

    \item T2TRG meeting on Friday
  \end{description}
\end{frame}

\begin{frame}{Do we really need \texttt{coap+foo}?}\large
  Ambiguous: \texttt{coap://$\underbrace{\texttt{[2001:db8::1]:1234}}_{\textsf{TCP port? UDP port?}}$/}

  Clarified: \texttt{coap+tcp://[2001:db8::1]:1234/}

  \bigskip

  Unambiguous:
  \begin{itemize}
    \item \texttt{coap://0123456789ab.ble.arpa/} (was \texttt{coap+ble://\ldots})
    \item \texttt{coap://7.6.5.4.3.2.1.5.5.5.3.4.e164.arpa/} (was \texttt{coap+sms://+43555\ldots})
    \item \texttt{coap://ttyUSB0.uart.tbdlocal.arpa/}\footnote{Or \texttt{ttyUSB0.alt}?} % as long as components can recognize it's locally significant
    \item \texttt{coap://001.004.usb.tbdlocal.arpa/}
  \end{itemize}

  \bigskip

  Criterion: \texttt{coap+foo} needed if the literal for of authority values are ambiguous with respect to transports. Or if the resolution process produces such values.
\end{frame}

\begin{frame}{Proposal to update \texttt{transport-indication}}\large
  \begin{itemize}
    \item Recommend not adding \texttt{coap+x} schemes unless criterion is met.
  \end{itemize}

  \begin{block}{Doesn't this create aliasing?}
    No. It's only aliasing when differert URIs point to the same resource.

    Whether a server uses the same name for different transports or not is up to the operator.
  \end{block}

  \bigskip

  \ldots and CoAP-over-GATT (and slipmux?) will follow.\footnote{No development is known to be going on with the other transports.}
\end{frame}

\begin{frame}{Can't just rely on literals!}\large
  \framesubtitle{How do I know what to do with \texttt{coap://c.example.com}?}

  Naming systems provide metadata.

  \bigskip

  \texttt{{\color{gray}\$} dig c.example.com}\\
  \texttt{c.example.com. 32000 IN AAAA $\underbrace{\texttt{2001:db8::42}}_{\textsf{insufficient literal\footnotemark[1]}}$}\footnotetext[1]{The literal is OK on its own, but insufficient when combined with just a port.}

  but

  \texttt{{\color{gray}\$} dig BLE c.example.com}\\
  \texttt{c.example.com. 32000 IN $\underbrace{\texttt{BLE\footnotemark[2]\quad 0123456789ab}}_{\textsf{Not much more, but has own discovery}}$}\footnotetext[2]{With no desire to do this here or precisely that way, but it would suffice.}
\end{frame}

\begin{frame}[fragile]{Other lookup systems can provide similar metadata}\large
  \framesubtitle{Extrapolating from \ietfdraft{core-resource-directory-extensions} for forward proxy setup}

\begin{verbatim}
GET coap://thedirectory.net/rd-lookup/
          ?anchor=coap://00publickey00.onion-ish.arpa

2.05 Content
Payload:
<coap+tcp://[2001:db8::5]/>;rel=has-proxy;
          anchor="coap://00publickey00.onion-ish.arpa"
\end{verbatim}
\end{frame}

\begin{frame}{Alternative history}\large
  \framesubtitle{If we had \rfc{9460} SVCB back when \rfc{8323} was done\footnote{CoAP over TCP was approved 2017-12-18, first \ietfdraft{schwartz-httpbis-dns-alt-svc} was published 2018-01-16}…}

  \texttt{{\color{gray}\$} dig SVCB \_coap.c.example.com}\\
  \texttt{c.example.com. 32000 IN SVCB 1 . transport="tcp"}\\
  \texttt{c.example.com. 32000 IN SVCB 2 . transport="udp" port=61616}\\
  \texttt{c.example.com. 32000 IN SVCB 3 . transport="udp"}

  \bigskip

  Adopt for future IP based transports;
  solves no problems for us any more unless anyone wants to deprecate \texttt{+tcp} and \texttt{+ws}.
\end{frame}

\begin{frame}{Going forward}\Large
  \begin{itemize}
    \item Gather any objections here.
    \item Update GATT and transport-interfaces drafts to not do \texttt{coap+x} unless criterion is met.
  \end{itemize}
\end{frame}

\end{document}
