\input{shared/ietf-slides.tex}

% about the presentation
\title[CoAP Transport Indication]{CoAP Transport Indication\footnote{Used to be Protocol Indication, document name was \texttt{transport-indication} already}}
\subtitle{\ietfdraft{ietf-core-transport-indication-05}}
\author{\textit{Christian~Amsüss}, Martine~Lenders}
\date{2024-03-20 \\CoRE at IETF 119 in Brisbane}

\begin{document}

\frame{\titlepage}

\begin{frame}{Goals}\Large
  \begin{enumerate}
    \item Enablement of transport discovery
    \item No Aliasing
    \item Optimization (no cost per request)
    \item Proxy usability
    \item Proxy announcement
  \end{enumerate}

  \bigskip

  \begin{itemize}
    \item Give way forward after \texttt{coap://} and \texttt{coap+tcp} diverged
  \end{itemize}
\end{frame}

\begin{frame}{Changes since IETF118}\large
  \framesubtitle{\textit{Why} did \texttt{coap://} and \texttt{coap+tcp} diverge? -- rehash of IETF118}

  Ambiguous: \texttt{coap://$\underbrace{\texttt{[2001:db8::1]:1234}}_{\textsf{TCP port? UDP port?}}$/}

  Clarified: \texttt{coap+tcp://[2001:db8::1]:1234/}

  \bigskip

  Unambiguous:
  \begin{itemize}
    \item \texttt{coap://0123456789ab.ble.arpa/} (was \texttt{coap+ble://\ldots})
    \item \texttt{coap://ttyUSB0.dev.alt/} (was \texttt{coap+uart://ttyUSB0/})
  \end{itemize}

  \bigskip

  Criterion: \texttt{coap+foo} needed if the literal for of authority values are ambiguous with respect to transports. Or if the resolution process produces such values.
\end{frame}

\begin{frame}{Changes since IETF118}\Large
  \begin{itemize}
    \item Guidance to new transports: \texttt{coap://}
      
      \ldots and if is IP based, do SVCB as described in the appendix E.

      \ldots and if you need that with IP literals, finish appendix F.
    \item Security guidence simplified
    \item Consistenlty talk of ``transports''
  \end{itemize}
\end{frame}

\begin{frame}{}\Huge
  \center
  IETF118 changes are applied.

  \bigskip

  Let's get this done\ldots
\end{frame}

\begin{frame}{Open question: Scope of \texttt{has-proxy}}\large
  ``only through link relations''

  \begin{itemize}
    \item URIs regarded as opaque
    \item Relations are explicit
    \item Allows to exclude indvidiual resources from transport indication
      \footnote{No support adding transport indication for individual resources is planned}
    \item Uses \rfc{6690} \texttt{rel=hosts} which is not very clear
    \item Hard to keep track of what works where
  \end{itemize}
  
  \begin{center}
  vs.
  \end{center}

  ``Applies per Origin''

  \begin{itemize}
    \item HTTP's mechanism
    \item Simple
    \item Way shorter wording in terminology section
  \end{itemize}
\end{frame}

\begin{frame}[fragile]{Open question: Self description style guide}\large
  \framesubtitle{e.\,g. after multicast discovery}

``Explicitly using canonical names''

\begin{verbatim}
<coap://myhostname/foo>,...,
<coap://[2001:db8::1]>;rel=has-unique-proxy;anchor="coap://myhostname"
\end{verbatim}

\begin{center}
vs.
\end{center}

``Relying on client to re-interpret the document after having parsed parts of it''

\begin{verbatim}
</foo>,...,
<coap://[2001:db8::1]>;rel=has-unique-proxy;anchor="coap://myhostname"
\end{verbatim}

  \bigskip

  \ldots Or do we not care so much about \rfc{6690} anyway,
    because other formats would allow setting a base anyway?
\end{frame}

\begin{frame}{Open question: Appendices}\Large
  \begin{itemize}
    \item Is alternative history fiction a thing here?
    \item (Where) should literals for service parameters (and other data from DNS) go?
  \end{itemize}
\end{frame}

\begin{frame}{Summary}\Large
  Open questions:
  \begin{itemize}
    \item Decide ``only through link relation'' vs ``always when Origin matches''
    \item Advertising self-proxies / importance of \rfc{6690}
    \item Fate of appendices
  \end{itemize}

  \bigskip
  
  What else before this is done?

  \bigskip

  Interop?
\end{frame}

\end{document}
