\input{shared/ietf-slides.tex}

% about the presentation
\title{CoAP Transport Indication}
\subtitle{\texttt{ietf-core-transport-indication-08}}
\author{\textit{Christian~Amsüss}, Martine~Lenders}
\date{CoRE interim, 2024-12-18}
\date{CoRE at IETF122 / Bangkok, 2025-03-18}

\begin{document}

\frame{\titlepage}

\begin{frame}{Recap: Mission}\Large
    \begin{itemize}
        \item Enable discovery of alternative transports

        \item Build a plan how new transports avoid new \texttt{coap+…}
    \end{itemize}
\end{frame}

\begin{frame}{Changes on enable-discovery}\framesubtitle{Following December interim}\Large
    \begin{itemize}
        \item Described more general components to use an endpoint:
            \begin{enumerate}\Large
                \item CoAP transport (eg. ``over TCP'')
                \item Address (eg. IP and port)
                \item Additional metadata
            \end{enumerate}
            \bigskip
        \item Describe available endpoint sources in those terms:
            \begin{enumerate}\Large
                \item Explicit links to proxies
                \item Resolution service, in particular DNS with A/AAAA and SVCB (\rfc{9460})
                \item \color{gray}Explicit configuration\footnote{not described}
            \end{enumerate}
    \end{itemize}
\end{frame}

\begin{frame}{Plan for new transports}\Large
    {\color{gray}
    ``Ensure that all components of endpoint are looked up''

    \bigskip

    For IP transports: Needs SVCB records.

    \bigskip

    Gap: Literals. \texttt{coap://[2001:db8::1]} misses lookup result.\footnote{
        \texttt{\_coap1.0…1.0.0.2.ip6.arpa IN SVCB alpn="coapquic"} is funny but not helpful.}
    }

    \vspace{1cm}

    Update to syntax; examples:
    \texttt{coap://636f617071756963.alpn.2001-db8--1.6.service.arpa/}
    \texttt{coap://rai3ouj4a.ueekca…zowjgyr-.cred.service.arpa/}
\end{frame}

\begin{frame}{Question: Fate of parts}\Large
    \begin{itemize}
        \item Some SVCB registrations being picked up elsewhere.
            \bigskip

            \texttt{edhoc-info} might move to \ietfdraft{tiloca-lake-app-profiles}

            \texttt{cred} needed to solve \ietfdraft{draft-lenders-core-dnr}\footnote{a problem statement document}

            \bigskip
        \item Do we need literals here? Who needs it now?\footnote{Why hard and slow? Needs explicit information model.}
            \begin{itemize}\Large
                \item Next IP-based transport.
                \item Onion CoAP \ietfdraft{amsuess-t2trg-onion-coap}.
            \end{itemize}
            \bigskip

        \item Can this complete without registered \texttt{.service.arpa}?
    \end{itemize}
\end{frame}

\begin{frame}{Other open points}\Large
    \begin{itemize}
        \item (Even) More precision needed on properties of SVCB records vs. properties of proxies.\footnote{Proxies can have properties independent of endpoint, might chain; SVCB has priorities and different fan-out.}
            % if need full details: SVCB can have multiple A/AAAA records and/or CNAME, proxy can have full set in chain that'd indicate an onion path
            \bigskip
        \item SVCB best practice (\texttt{\_coap SVCB} vs. \texttt{COAP} record, ALPN for non-TLS)
    \end{itemize}
\end{frame}

\begin{frame}{Next steps}\Huge
    Review.

    \vspace{2cm}
    
    \large
    Yes, we have more work to do; nonetheless, almost flying blind.
\end{frame}

\end{document}
