\input{shared/ietf-slides.tex}

% about the presentation
\title{CoAP Transport Indication}
\subtitle{\texttt{ietf-core-transport-indication-07}}
\author{\textit{Christian~Amsüss}, Martine~Lenders}
\date{IETF121 Dublin, CoRE, 2024-11-05}

\begin{document}

\frame{\titlepage}

\begin{frame}{What this document is about}\Large
    \begin{itemize}
        \item Describe how different CoAP transports can be used (automatically).
        \item Describe path forward on \texttt{coap+…} schemes.

            \bigskip

            This is a prerequisite for new standardized transports!\footnote{WIP: CoAP-over-GATT. Pondering in RIOT OS: CoAP-over-CAN. In use: CoAP-over-MQTT.}
    \end{itemize}
\end{frame}

\begin{frame}{Recent changes}\Large
    \begin{itemize}
        \item Restructuring
        \item Proxies are key; discoverable through
            \begin{itemize}\Large
                \item Links
                \item SVCB (now claimed more boldly)
                \item … or whatever else is around for a transport
            \end{itemize}
        \item Unified \texttt{\_coap} service (was \texttt{\_coaps} and \texttt{\_coap})
    \end{itemize}
\end{frame}

\begin{frame}{Steps to completion}\Large
    \begin{itemize}
        \item Find input for what are toss-up questions so far
            \begin{itemize}\Large
                \item \texttt{\_coap.dev.example.com IN SVCB} or \\ \texttt{dev.example.com IN COAP}?
                \item \texttt{alpn} or new \texttt{coaptransport} for non-TLS transports?
            \end{itemize}
        \item Jettison parts that slow it down?
            \begin{itemize}\Large
                \item SVCB parameters \texttt{edhoc-cred}/\texttt{-info} and \texttt{oauth-hints}
                \item ``IP literal with extra data'' appendix

                    Would leave small gap in future IP based transport story.
                \item ``Related applications'' appendix
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Where should literals go?}\Large
    Currently in appendix.
    
    \bigskip

    Examples\footnote{Precise syntax is not fixed or even fully consistent.}:

    \normalsize

    \bigskip

    \texttt{https://tlsa.amaqckrkfivcukrkfivcukrkfivcukrkfivcukrkfivcukrkfivcukrk\\\qquad.service.arpa/}

    \bigskip

    ``has no A/AAAA record but a TLSA record with certificate usage 3'' (no CA/PKIX needed)

    \vspace{1cm}

    \texttt{coap://svcb.alpn\_coapquic.6.2001-db8--1.service.arpa/temperature}

    \bigskip

    ``has an AAAA record and SVCB parameters''
\end{frame}

\begin{frame}{Next steps}\Large
    \begin{itemize}
        \item Gather WG input.
        \item Finalize down document based on that.
    \end{itemize}
\end{frame}

\end{document}
